---
title: 'Using CourseKata Data'
date: 'Last updated: `r Sys.Date()`'
output: 
  github_document: default
  pdf_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = '.', output_format = 'all') })
suppress_badges: TRUE
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Getting Started

*Note: This file is included in all data downloads for completed courses on [CourseKata](https://coursekata.org).*

The easiest way to get up and running with class data from our course is to use our custom R package 'CourseKataData' which can be found at <https://github.com/UCLATALL/CourseKataData>. The package will unpack and pre-process the data for you to make it a little more manageable. If you aren't comfortable with using R, we still recommend that you use this package to process the data before continuing with your preferred statistical methods. 

The absolute simplest way to get running is only a few lines of code in R:

```{r, eval=FALSE}
# install a package to install the processing package
install.packages('devtools')

# install the processing package
devtools::install_github('UCLATALL/CourseKataData')

# load the package
library(CourseKataData)

# process the data (change the path to point to your downloaded zip file)
process_data('path/to/your/data')
```

By default, the data will be loaded into R objects. R has a number of tools for exporting objects to standard formats. A common format that can be read by most programs (including Excel, Stata, SAS, SPSS) is the comma-separated value (CSV) format. You can export to CSV format with the following code:

```{r, eval=FALSE}
write.csv(responses, 'path/to/save/the/csv/to', na = '', row.names = FALSE)
# responses is only one of the objects that is created by process_data()
# make sure you export all the data you need
```

## More Detail

The rest of this document is the full README that is included on the 'CourseKataData' repository. In addition to explaining some of the other functions in the package, there is a section that explains each of the variables in each of the downloaded data files (**Data Structure**).

<br> <br> ------------------------------------------------------------ <br> <br>

`r knitr::knit_child('README.Rmd', envir = rlang::env(suppress_badges = TRUE))`
